Referee report checklist

### 2021-01-27 Revision/list.tex
made what I am hoping is the last or second to last round of edits. Please look over carefully.

\response{Sorry for not making it clear. The estimation procedures can be explained in detail as follows. Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \textcolor{red}{\mathbf{Y}_i^{(1)}}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series, $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$, \textcolor{red}{and  $\mathbf{Y}_i^{(1)}$ is the lagged response $\mathbf{Y}_{i}=(y_{i,1},\ldots,y_{i,T_i})'$}. We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \textcolor{red}{\mathbf{Y}_i^{(1)}}, \mathbf{X}_{i})$. Then the expression for $\hat{\alpha}_i$ is
\begin{align*}
  \hat{\alpha}_i = [(\mathbf{M}'_i\mathbf{M}_i)^{-1}\mathbf{M}_i'\mathbf{Y}_{i}]_{2}, 
 \quad  \text{ for } i = 2, \ldots, n+1,
\end{align*}
where $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Our model is
\begin{align*}
  y_{i,t} = \eta_i + \alpha_i D_{i,t} + \phi_i y_{i,t-1} + \theta_i'\mathbf{x}_{i,t} + \varepsilon_{i,t}, 
  \quad i = 1, \ldots, n+1.
\end{align*}
$\eta_i$ represents the effect of the intercept. Thus, we cannot identify $\alpha_i$ from $\eta_i$. As defined in (4) in the manuscript, through averaging, $\hat{\alpha}_{\rm adj}$ is an estimator  of $E(\alpha_1)$.} \\

@@

\response{Thanks for pointing it out. We  clarify it in the revised version, and change the notation to be $\mathbf{M}_i$, which represents the design matrix of the model used in OLS estimation at the $i$th time series.} \\

@@

\response{\textcolor{red}{To our best knowledge, it is impossible to justify this assumption.} % Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects. If this cannot be done, then the methodology may not work well. 
\textcolor{red}{In real-life applications,} practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool. Consider our Conoco Phillips example. On March 9th 2020, Conoco Phillips was expected to experience a negative shock in the midst of the  COVID-19 pandemic and an oil supply shock. While the COVID-19 pandemic is unprecedented, several economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises. On the other hand, the oil supply shock had precedent. As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.} \\

@@

\response{Yes. It could be a restrictive assumption in a number of situations. Panel data applications are ruled out. Additionally, if time series in a donor pool are observed in almost concurrent time as the one under study (or, the time differences are not large enough), the independence assumption may not hold. However, if the time differences between the time series under study and those forming the donor pool are large enough, then the dependence should be negligible. This is the case in our Conoco Phillips and Apple examples.} \\

@@

\textcolor{red}{Our proposed methodology is applied at $T_1^*+1$, yielding gains over the unadjusted forecast.} You are right about the timing. Our methodology can be applicable in many different timing scenarios. Generally, suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$ and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. It is possible to generalize our method to this situation. Our new Apple example in Section 5.2 of the revised manuscript provides an example for the case $d=2$ with predicted covariates. \\

Thank you for your remark on the timing scenarios. It is very helpful for improving our manuscript.} \\

@@

\response{It is a very good point. Thanks for pointing it out. Indeed, our method assumes $\mathbf{x}_{1, T_1^* + 1}$ to be given. If it is to be forecasted with errors, it will possibly result in a biased estimation of $E(\alpha_1)$ with $\hat{\alpha}_{\rm wadj}$ such that the evaluation of the proposition may not be reliable. \\

In fact, the situation when  covariates are forecasted with errors is similar to the one when the variance of the shock effect is large. In both situations, the signal from covariates is weak. Our simulation discusses this situation by increasing $\sigma_{\alpha}$. It shows that a slightly weak signal will not compromise the correctness of our evaluated propositions a lot. However, if the forecast for the covariates is seriously bad (i.e., the signal from covariates is really weak), our result shows that the risk-reduction evaluation may be only as good as a random guess. \\

In the event that the mean shift $D_{i,t}$ interacts with the covariates, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions. In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed. A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid. This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid. \textcolor{red}{This  gives users a sense of variability of post-shock predictions due to forecast error from covariates.}} \\

@@

It is possible to use the donor pool to estimate the shock transition,  and produce an intercept dummy for the next $m$ periods. Assume there are no additional shocks  after $T_1^*+1$, and $T_i^*+m \leq T_i$ for $i = 2, \ldots, n+1$. Consider the model
\begin{align*}
  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i, T_i^* + d}I(t = T_i^*+d) +\varepsilon_{i,t}
\end{align*}
for $i = 2, \ldots, n+1$ and $d = 1, \ldots, m$. Suppose we have information of the covariates up to $T_1^*+d$ either by given information or by forecasting. We can use our proposed synthetic control method to compute weights $\mathbf{W}^*$ and OLS to estimate $\beta_{i, T_i^*+d}$ to compute $\hat{\beta}_{1, T_1^*+d}$.  As a result, we obtain $\hat{\boldsymbol{\beta}}_1^{(m)} = (\hat{\beta}_{1, T_1^*+d})_{d = 1}^m$. However, it cannot be a simple intercept dummy but instead an iterative adjustment in computing $m$-ahead forecasts. For example, $\hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)}+ \hat{\beta}_{1, T_1^*+2}$, where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts. %considering $\hat{y}_{1, T_1^*+1}^{(1)}$ in computation.  
\textcolor{red}{One can then use $\hat{\boldsymbol{\beta}}_1^{(m)}$ to judge whether the shock is transitory  or permanent.} The approach of \cite{agarwal2020two} is an alternative  to \textcolor{red}{intercept correction dummy} problem though its adjustment is without theoretical guarantees. \\

%To judge if the shock is permanent, we may consider another approach. Consider the model
%\begin{align*}
%  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i}I(T_i^*< t \leq  T_i^*+d) +\varepsilon_{i,t}.
%\end{align*}
%We can compute $\hat{\beta}_i$ from OLS and $\mathbf{W}^*$ from synthetic approach with covariates $d \times p$ (see for example of $p = 2$ in our added Apple example in Section 5.2 of revised transcript) to compute $\hat{\beta}_1$. Note that $\hat{\beta}_1$ is unbiased. We can use parametric double bootstrap to test the hypothesis that $H_0 \colon \beta_1=0$ versus $H_1 \colon \beta_1\neq 0$ at time point $T^*_i+d$. \\

To the best of our knowledge, we don't know whether the theoretical statements of our proposed methods in the manuscript can be adapted to assess when transitory shocks die out. This is beyond the scope of our current paper.} \\

>>>>

\response{Sorry for not making it clear. The estimation procedures can be explained in detail as follows. Note that for $i = 2, \ldots, n+1$, the design matrix for $i$th time series is $(\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{Y}_i^{(1)}, \mathbf{X}_{i})$, where $\mathbf{X}_i$ is the covariates  of $i$th time series, $\mathbf{D}_{i}\in\R^{T_i}$ with $D_{i,t}=I(t=T_i^*+1)$, and $\mathbf{Y}_i^{(1)}$ is the lagged response $(y_{i,1},\ldots,y_{i,T_i})'$. We define $\mathbf{M}_i = (\mathbf{1}_{T_i}, \mathbf{D}_{i}, \mathbf{Y}_i^{(1)}, \mathbf{X}_{i})$. Then the expression for $\hat{\alpha}_i$ is
\begin{align*}
  \hat{\alpha}_i = [(\mathbf{M}'_i\mathbf{M}_i)^{-1}\mathbf{M}_i'\mathbf{Y}_{i}]_{2}, 
 \quad  \text{ for } i = 2, \ldots, n+1,
\end{align*}
where $[\cdot]_{2}$ denotes the second element of a vector. That is, $\hat{\alpha}_i$ is the second element of the OLS estimate vector. Our model is
\begin{align*}
  y_{i,t} = \eta_i + \alpha_i D_{i,t} + \phi_i y_{i,t-1} + \theta_i'\mathbf{x}_{i,t} + \varepsilon_{i,t}, 
  \quad i = 1, \ldots, n+1.
\end{align*}
the intercept is denoted as $\eta_i$. Thus, we cannot identify $\alpha_i$ from $\eta_i$. As defined in (4) in the manuscript, through averaging, $\hat{\alpha}_{\rm adj}$ is an estimator  of $E(\alpha_1)$.} \\

@@

\response{Thanks for pointing it out. This quantity is the model (design) matrix corresponding to the $i$th time series. We clarify this quantity the revised version, and we change the notation to be $\mathbf{M}_i$. Our previous response describes $\mathbf{M}_i$ in more detail.} \\

@@

 Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects. If this cannot be done, then the methodology may fail. In real-life applications, practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool. Consider our Conoco Phillips example. On March 9th 2020, Conoco Phillips was expected to experience a negative shock in the midst of the  COVID-19 pandemic and an oil supply shock. While the COVID-19 pandemic is unprecedented, several, although not all, economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises. On the other hand, the oil supply shock had precedent. As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock. \\

@@

\response{Yes. It could be a restrictive assumption in a number of situations. Panel data applications are ruled out. Additionally, if time series in a donor pool are observed in almost concurrent time as the one under study (or, the time differences are not large enough), the independence assumption may not hold. However, if the time differences between the time series under study and those forming the donor pool are large enough, then the dependence should be negligible. This is the case in our Conoco Phillips and Apple examples. We include this discussion in the Introduction. Thank you for this comment.} \\

@@

Our proposed methodology is applied at $T_1^*+1$. You are right about the timing. Our methodology can be applicable in many different timing scenarios. Generally, suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$ and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. It is possible to generalize our method to this situation. Our new Apple example in Section 5.2 of the revised manuscript provides an example for the case $d=2$ with predicted covariates. \\

Thank you for your remark on timing scenarios, it led to an improved manuscript.} \\

@@

\response{Good point, thank you. Indeed, our method assumes $\mathbf{x}_{1, T_1^* + 1}$ to be given. If it is to be forecasted with errors, it will possibly result in a biased estimation of $E(\alpha_1)$ with $\hat{\alpha}_{\rm wadj}$ such that the evaluation of the proposition may not be reliable. \\

The situation when covariates are forecasted with errors is similar to the one when the variance of the shock effect is large. In both situations, the signal from covariates is weak. Our simulation discusses this situation by increasing $\sigma_{\alpha}$. It shows that a slightly weak signal will not strongly compromise the correctness of our prospective methods. However, if the forecast for the covariates is seriously bad (i.e., the signal from covariates is really weak), our result shows that the risk-reduction evaluation may be only as good as a random guess. \\

In the event that the mean shift $D_{i,t}$ interacts with the covariates, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions. In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed. A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid. This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid. This may gives users a sense of the variability of post-shock predictions due to forecast error from covariates that are also affected from the shock. We included this response to the Discussion, thank you again.} \\

@@

It is possible to use the donor pool to estimate the shock transition,  and produce an intercept dummy for the next $m$ periods. Assume there are no additional shocks  after $T_1^*+1$, and $T_i^*+m \leq T_i$ for $i = 2, \ldots, n+1$. Consider the model
\begin{align*}
  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i, T_i^* + d}I(t = T_i^*+d) +\varepsilon_{i,t},
\end{align*}
for $i = 2, \ldots, n+1$ and $d = 1, \ldots, m$. Suppose we have information of the covariates up to $T_1^*+d$ either by given information or by forecasting. We can use our proposed synthetic control method to compute weights $\mathbf{W}^*$ and OLS to estimate $\beta_{i, T_i^*+d}$ to compute $\hat{\beta}_{1, T_1^*+d}$.  As a result, we obtain $\hat{\boldsymbol{\beta}}_1^{(m)} = (\hat{\beta}_{1, T_1^*+d})_{d = 1}^m$. However, it cannot be a simple intercept dummy but instead an iterative adjustment in computing $m$-ahead forecasts. For example, 
$$
  \hat{y}_{1, T_1^*+2}^{(1)}=\hat{y}_{1, T_1^*+2}^{(0)} + \hat{\beta}_{1, T_1^*+2}, 
$$
where $\hat{y}_{1, T_1^*+2}^{(0)}$ is the standard 2-ahead forecasts. One then may be able to use $\hat{\boldsymbol{\beta}}_1^{(d)}$ to judge whether the shock is transitory or permanent. We speculate that the transitory shock effect can be theoretically justified using similar arguments as those that appear in our manuscript, but we view this extension as outside the scope of our current paper. The SCM based approach of \cite{agarwal2020two} is an alternative that may also be able to assess whether or not a shock is transitory, although this adjustment is without any theoretical guarantees. \\

%To judge if the shock is permanent, we may consider another approach. Consider the model
%\begin{align*}
%  y_{i,t} = \eta_i + \theta_i'\mathbf{x}_{i,t} + \phi_i y_{i,t-1 }+\beta_{i}I(T_i^*< t \leq  T_i^*+d) +\varepsilon_{i,t}.
%\end{align*}
%We can compute $\hat{\beta}_i$ from OLS and $\mathbf{W}^*$ from synthetic approach with covariates $d \times p$ (see for example of $p = 2$ in our added Apple example in Section 5.2 of revised transcript) to compute $\hat{\beta}_1$. Note that $\hat{\beta}_1$ is unbiased. We can use parametric double bootstrap to test the hypothesis that $H_0 \colon \beta_1=0$ versus $H_1 \colon \beta_1\neq 0$ at time point $T^*_i+d$. \\
} \\
